I cannot imagine a place where I would have rather spent my PhD years than the MPI-IE. Representatively, I would like to thank the entire Akhtar Group, the Bioinformatics Group and the Deep Sequencing Unit at the MPI-IE -- for endless, fruitful discussions about everything, and for being awesome peers! All my projects were collaborative projects in the best sense and none of them would have been accomplished without the work and insights from everyone involved.I am especially indebted to:\textbf{Asifa} who had so much faith in my abilities that did not even exist at the beginning of my PhD, gave me all the support and freedom that I needed to find my way into the bioinformatics community, inspired and motivated me without end with her enthusiasm.\textbf{Fidel} who first helped me lose my feaR and then pushed me towards python, eagerly discussed tedious problems and details, enabled me (and many others) to do analyses faster and more impressively than I would have ever imagined, always takes initiative and seeks solutions rather than work-arounds, and makes the most delicious veggie sticks.\textbf{Ken} who introduced me to ChIP-seq analysis, the NSL complex and everything else I needed to know, who never ran out of sharp insights, clever questions and new analyses and who truly impressed me with his honest passion for science. I don't know if I had ever become a computational biologist without his help and inspiration.\textbf{Sarah} who painlessly introduced me to the UNIX shell and scripting, installed countless stubborn programs, sat with me for hours hunting other people's code bugs, masters the Galaxy, tames the servers and tirelessly fights back the rising chaos of increasing data and people messing with it, and, most importantly, selflessly ensures a constant supply of Luxemburgian coffee pads.\textbf{Thomas} who let me become part of the bioinformatics group despite my utter lack of bioinformatics savvy in the beginning, whose support I could always, always count on, whose one-on-one supervision was absolutely essential for the success of my very first bioinformatic steps and without whom I still would have never driven a go-kart.\textbf{Tomek} who trusted me with his data, was a constant source of inspiring ideas, made the most beautiful illustrations and always brought exquisite delicacies from Poland and Paris.I would also like to thank Andrew Pospisilik and Michael Stadler who supported me during TAC meetings and beyond. I couldn't have had a better TAC!